Inferring the Recombinant Genealogy of a Pandemic Pathogen in Real Time

### 2025-09-13 latex/main.tex
Fixup table alignment

>>>>

\newcommand{\cprheight}{4.0em}

\begin{figure}
\centering
% NOTE the size of the second "m" column doesn't matter, but we have to fix the
% size in order for vertical centering to work :sigh:
% The layout here isn't ideal, but it's incredibly fiddly to get center
% alignment veritically with cells to work, so this is good enough.
\begin{tabularx}{0.85\textwidth}{>{\centering\arraybackslash}m{1cm}>{\arraybackslash}m{1cm}}
% FIXME: these samples are chosen randomly and so almost certainly do not
% belong to the correct quadrants.
A & \includegraphics[height=\cprheight]{static/causedby-ERR10306608.png}\\
B & \includegraphics[height=\cprheight]{static/causedby-ERR6760245.png}\\
C & \includegraphics[height=\cprheight]{static/causedby-SRR15864165.png}\\
D & \includegraphics[height=\cprheight]{static/causedby-SRR21087725.png}\\
\end{tabularx} 
\caption{Examples of problematic copying patterns. A-D are examples drawn from
the labelled quadrants in Figure~\ref{fig:recombinant_qc}.}
\label{fig:copying_pattern_examples}
\end{figure}

\renewcommand{\cprheight}{1.5em}
% Add some more space between rows. Note this it would be sligntly nicer if the 
% label was aligned vertically in the center of the row, but this is good
% enough for now.
\renewcommand{\arraystretch}{2}

\begin{figure}
\centering
\begin{tabularx}{\textwidth}{>{\centering\arraybackslash}m{1cm}>{\arraybackslash}m{1cm}}
XC & \includegraphics[height=\cprheight]{static/XC.png}\\
XBR & \includegraphics[height=\cprheight]{static/XBR.png}\\
XA & \includegraphics[height=\cprheight]{static/XA.png}\\
XS & \includegraphics[height=\cprheight]{static/XS.png}\\
XL & \includegraphics[height=\cprheight]{static/XL.png}\\
XBG &\includegraphics[height=\cprheight]{static/XBG.png}\\
XBD & \includegraphics[height=\cprheight]{static/XBD.png}\\
XQ & \includegraphics[height=\cprheight]{static/XQ++.png}\\
XBB & \includegraphics[height=\cprheight]{static/XBB.png}\\
XM & \includegraphics[height=\cprheight]{static/XM+XAL.png}\\
XBF & \includegraphics[height=\cprheight]{static/XBF.png}\\
XF & \includegraphics[height=\cprheight]{static/XF.png}\\
XY & \includegraphics[height=\cprheight]{static/XY.png}\\
XG & \includegraphics[height=\cprheight]{static/XG.png}\\
XW & \includegraphics[height=\cprheight]{static/XW.png}\\
Xx & \includegraphics[height=\cprheight]{static/XZ++.png}\\
XE/XH  & \includegraphics[height=\cprheight]{static/XE+XH.png}\\
XBH & \includegraphics[height=\cprheight]{static/XBH.png}\\
XBM & \includegraphics[height=\cprheight]{static/XBM.png}\\
XJ & \includegraphics[height=\cprheight]{static/XJ.png}\\
\end{tabularx}
\caption{Copying patterns for the 20 recombination events associated with Pango 
X lineages listed in Table~\ref{tab:pango_x_lineages} (in the same order)}
\label{fig:pango_x_copying_patterns}
\end{figure}

% Reset this in case we make any more tables beyond this
\renewcommand{\arraystretch}{1}
